\LARGE\singlespacing{\textbf{Supplementary Material} \\ \medskip Molecular detection of SARS-CoV-2 and other respiratory viruses in saliva and classroom air: a two winters tale}

### 2024-02-16 doc/comparison-mcid12/supplements.tex

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

>>>>

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/comparison-viral-loads.png}
    \caption{Comparison of Ct values for positive saliva samples between SARS-CoV-2 (CoV) and non-SARS-CoV-2 (non-CoV) viruses. A statistical comparison was performed pooling the Ct values across the two study periods (winter 2021/22 and 2022/23), with the p-value (p) based on a numerical two-sided two sample t-test.}
    \label{fig:viral-loads}
\end{figure}
